Gammapy: A Python package for gamma-ray astronomy

### 2022-12-03 src/ms-review.tex
Move SWH paragraph

>>>>

In addition \gammapy is also listed in the Software
Heritage\footenote{\url{https://www.softwareheritage.org/}} (SWH) archive~\cite{DBLP:conf/icms/Cosmo20}.
The archive  collects, preserves, and shares the source code of publicly available software.
SWH automatically scans open software repositories, like e.g. GitHub, and projects are archived in SWH by the
means of SoftWare Heritage persistent IDentifiers (SWHID), that are guaranteed to remain stable (persistent)
over time. The French open publication archive, HAL~\footenote{\url{https://hal.archives-ouvertes.fr/}},
is using the \gammapy SWHIDs to register the releases as scientific
products \footenote{\url{https://hal.archives-ouvertes.fr/hal-03713410v1}} of open science.
